---
title       : An Introduction to R
subtitle    : 
author      : Dan Martin
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
  user: dpmartin42
  repo: R-Intro
---

## Overview

1. What is R?

2. Basic Commands

3. Cleaning

4. Plotting

5. Reproducible Research 

--- 

## What is R


Available at http://cran.r-project.org

* A statistical language
* A programming language
* Object-oriented
  * everything is an object in R

--- 

## Why use R?

* It's free!
* It's open source
  * You can see, re-use, and modify code as needed
* It's flexible
* Access to > 5000 packages
* Can easily create data products

--- 

## A major con...

* It's tough!

My goal today is to focus on *your* needs as applied researchers

--- 

## Some useful R packages for reference

* Any type of general linear model: Base
* Logistic Regression: glm
* Structural equation modeling: OpenMx, lavaan
* Multi-level models: lme4, nlme
* Latent Class/Profile Analysis: poLCA, mClust
* Survey Weights: survey
* Propensity Scores: Matching, MatchIt
* Multiple Imputation: mice
* Graphics: ggplot

--- 

## Some cool examples
## Interactive plots with Shiny

[SPR Cup Global Health Project](https://dpmartin42.shinyapps.io/App-1/)

--- 

## Some cool examples
# Interactive plots with Shiny

[Dialect Maps](http://spark.rstudio.com/jkatz/SurveyMaps/)

--- 

## Some cool examples
# Interactive plots with googleVis

```{r, echo = FALSE, results = 'asis', message = FALSE}

require(googleVis)

M1 <- gvisMotionChart(Fruits, idvar="Fruit", timevar="Date", options = list(width = 550, height = 350))
print(M1, tag = 'chart')

```

---

## Some cool examples
# Interactive plots with googleVis

```{r, echo = FALSE, results = 'asis', message = FALSE}

require(datasets)

states <- data.frame(state.name, state.x77)
M2 <- gvisGeoChart(states, "state.name", "Illiteracy",
                          options=list(region="US", 
                                       displayMode="regions", 
                                       resolution="provinces",
                                       width=550, height=350))

print(M2, tag = 'chart')

```

---

## Before we get started...

1. Download the latest version of R for your operating system
2. Install R Studio
3. Download the materials from ???



